How Do Like and Dislike Buttons Affect Communication?

### 2020-04-17 docs/analyses/analyses.Rmd
- initalize GitHubPages

---
title: "How Do Like and Dislike Buttons Affect Communication?"
shorttitle : "Analyses"
---

@@

```{r}
cooks_dis <- gCD(d, model_baseline)
plot(cooks_dis)
```

@@

```{r}
infl_cases <- invisible(rownames(print(cooks_dis)))
```

@@

```{r}
infl_cases_tokens <- d[infl_cases, "case_token"] %>% as_vector()
d %>% 
  filter(case_token %in% infl_cases_tokens) %>% 
  select(case_token, GR01_01:SE01_06, topics_entered:reactions, -SO01_01, TIME_SUM_t1, TIME_SUM_t2) %>% 
  kable() %>% 
  kable_styling("striped") %>% 
  scroll_box(width = "100%")
```

@@

```{r SaveData, include=F, cache=F}
write.csv(d, file = "data/data.csv", row.names = FALSE)
save(d, d_raw, d_all, d_fs,
     fit_baseline, fit_prereg, fit_adapted, fit_simple,
     fig_fs_m, fig_fs_cor, fig_coeffs,
     des_pridel,
     model_comp_tab, factor_val_tab,
     n_comments, n_desired, n_posts, n_speeding, n_time, n_words,
     n_comments, n_words, n_time, n_posts, n_speeding,
     n_users, n_final,
     infl_cases, infl_cases_tokens, resp_pattern, n_resp_pattern,
     n_t1, age_t1_m, male_t1_m, college_t1_m,
     n_t2, age_t2_m, male_t2_m, college_t2_m,
     n_matched, n_final, age_final_m, male_final_m, college_final_m,
     r_sesoi, r_sensitive, power_achieved,
     rsquare_fit_prereg, rsquare_fit_adapted, rsquare_fit_simple,
     file = "data/workspace.RData"
     )
```

>>>>

---
title: "How Do Like and Dislike Buttons Affect Communication?"
shorttitle : "Analyses"
output: 
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    keep_md: true
---

@@

```{r eval=F}
cooks_dis <- gCD(d, model_baseline)
plot(cooks_dis)
```

@@

```{r eval=F}
infl_cases <- invisible(rownames(print(cooks_dis)))
```

@@

```{r eval=F}
infl_cases_tokens <- d[infl_cases, "case_token"] %>% as_vector()
d %>% 
  filter(case_token %in% infl_cases_tokens) %>% 
  select(case_token, GR01_01:SE01_06, topics_entered:reactions, -SO01_01, TIME_SUM_t1, TIME_SUM_t2) %>% 
  kable() %>% 
  kable_styling("striped") %>% 
  scroll_box(width = "100%")
```

@@

```{r SaveData, include=F, cache=F}
write.csv(d, file = "data/data.csv", row.names = FALSE)
save(d, d_raw, d_all, d_fs,
     fit_baseline, fit_prereg, fit_adapted, fit_simple,
     fig_fs_m, fig_fs_cor, fig_coeffs,
     des_pridel,
     model_comp_tab, factor_val_tab,
     n_comments, n_desired, n_posts, n_speeding, n_time, n_words,
     n_comments, n_words, n_time, n_posts, n_speeding,
     n_users, n_final,
     # infl_cases, infl_cases_tokens, 
     resp_pattern, n_resp_pattern,
     n_t1, age_t1_m, male_t1_m, college_t1_m,
     n_t2, age_t2_m, male_t2_m, college_t2_m,
     n_matched, n_final, age_final_m, male_final_m, college_final_m,
     r_sesoi, r_sensitive, power_achieved,
     rsquare_fit_prereg, rsquare_fit_adapted, rsquare_fit_simple,
     file = "data/workspace.RData"
     )
```
